\documentclass[]{article}

\usepackage{hyperref, amsmath}
\hypersetup{
    colorlinks,
    citecolor=black,
    filecolor=black,
    linkcolor=black,
    urlcolor=black
}

\begin{document}


\title{An Amazingly Captivating Title}
\author {Best Author $\rightarrow$ Nancy Pham  $\leftarrow$  Super cool}

\maketitle

\newpage
\tableofcontents
\newpage

\section{Abstract}
Let's summarize our findings here in a very concise manner! But in the mean time I'm just going to write a ton about nothing so we can pad this out a little bit. Because of course what would our test thesis look like if it was just random headings with no content? Clearly that just won't do, but I digress I'd just like to comment on the fact that I went to bed at 4am last night; that's unheard of for me! You should be so proud of yourself for keeping such a morning person like me awake so close to my usual wake up time. Having said all this the conclusion is quite obvious, I regret nothing and that was a wonderful evening!

\section{Introduction}
Here's where the intro shall go! That's right I'm going to attempt to type about pretty well nothing for a good 5-10 minutes so that the paper actually has some padding to it. Not only does this serve as a bit of entertainment for me, but hopefully it'll at least crack a smile on your face! Can we just reflect on the fact that your roommates are amazing? Literally not 30 seconds after walking through the door I'm greeted by Kaiden straight up in my face asking me if I like Pokemon. I was so set back, but at the same time I was like well alright then I guess he's already accepted me haha! Sienna is so different from her brother though, wow. She seems really quiet and reserved, but they're only one year apart right? I do wish I had gotten a chance to talk to Papa and ... oh no, I forgot the other one! Was it Daddy? Oof, I'm really bad at this whole name thing. Regardless I would have liked to learn more about them, they seem like really interesting guys! Not to mention really fantastic at playing the piano... hold up, you could have played a song or two for me when they went swimming! What a missed opportunity, noooooo! Ok, next time we'll have a piano recital, but I'll go first so you can feel better about yourself haha Also can we just talk about the fact that those two rascals swim too, I love that! Perhaps I'm slightly biased here, but what a great activity to involve one's kids in :) Overall what a fantastic night! Now we just need to figure out what to do for our adventure next week, assuming you survive this Waterloo trip :( I say we do a combination of fabric shopping, pastries and perhaps one other activity depending on the weather! I'm itching to review another sewing related store to up my google local guide prestige haha Alright how are we doing with the length of this intro? Funnily enough this might even be longer than my actual Masters' projects' intros... speaking of which I might have lost those. Wait, I think they live on my dropbox account, I must investigate... Nope, looks like my account got deleted, sad days! Oh well, I wasn't very proud of them anyways haha Ok I lied, (No, not about the pastry!) I liked my math project, it was terribly written in Java, but I managed to solve a Chess related issue using three dimensional matrices. Oh yes, it's as nerdy as you think it is and then some... I had quite a lot of fun with that project! You know what, my second project was pretty cool too it was just the last one that I despised... Funny story the professor actually used me as an example of what not to do one of his classes lol You've gotta remind me of this story so I can do it justice! Alright how are we doing, nice we've made it past the first page and I've essentially written about nothing at this point. If you've made it this far through my random blabbering bravo I owe you a sheet of freshly baked peanut butter cookies.

\section{Literature review}
Save us from the most boring part of the entire paper! How many papers do you think is enough? Hmmm I ran out of sassy paper titles after 5 so we're just going to go with the arbitrary length for the time being haha
\subsection{Book One, Best Book}
Here's where we learn how to find ourselves through sewing! \cite{nancyBook}
\subsection{Paper 2 Again Amazing stuff}
We've got some quality content here! \cite{nancyArticle}
\subsection{Paper 3 marginally realted paper }
Ok... these papers are getting pretty bad now \cite{adamArticle}
\subsection{Paper 4 starting to reach now!}
Oof \cite{adamArticle2}
\subsection{Book 5 Totally unrelated fluf}
Frofy, fluffly padding \cite{adamBook}

\newpage
\section{Methods}
\subsection{Cool Mathy Things}
\subsection{Cat pictures!}
\subsection{Boring Math things}

\newpage
\bibliography{sources}
\bibliographystyle{ieeetr}

\end{document}